Random Generation of Rich \\ Abstract Data Type Values

### 2019-03-12 paper/synthesis.tex
Preparing for camera-ready version

We characterize the numbers of constructors that a random generator produces in
the $n$-th generation as a vector $G_n$, a vector that groups the number of
constructors of each kind produced in that generation---in our |Html| example,
this vector has four components, i.e., one for each constructor.
%
%We note $G_n$ to the vector of real numbers that represents the distribution of
%
From branching processes theory, the following equation captures the expected
distribution of constructors at the generation $n$, noted $E[G_n]$, as follows:
%
\begin{align}
  E[G_n]^T = E[G_0]^T \cdot M^n
  \label{eqn:prediction}
\end{align}

Vector $E[G_0]$ represents the initial distribution of constructors that our
generator produces, which simply consists of the generation probability of each
one.
%
The interesting aspect of the prediction mechanism is encoded in the matrix $M$,
known as a the \emph{mean matrix} of this stochastic process.
%
$M$ is a squared matrix with as rows and columns as different data constructors
involved in the generation process.
%
Each element $M_{i,j}$ of this matrix encodes the average number of data
constructors of kind $j$ that gets generated in a given generation, provided that we
generated a constructor of kind $i$ at the previous one.
%
In this sense, this matrix encodes the ``branching'' behavior of our random
generation from one generation to the next one.
%
Each element of the matrix can be automatically calculated by exploiting ADT
definitions, % \cite{DBLP:conf/haskell/MistaRH18}
%
% ---specially the recursive fields---
%
as well as the individual probability of generating each constructor.
%
For instance, the average number of |Text| data constructors that we will
generate provided that we generated a |Join| data constructor on the previous
level is calculated as follows:
%
$$ M_{\mathrm{Join, Text}} = 2\cdot p_{\mathrm{Text}} $$
%
where $2$ is the number of holes present when generating a partial ADT value
|Join| (i.e., |Join hole hole|) and $p_{\mathrm{Text}}$ is the probability of
individually generating the constructor |Text|.
%
This reasoning can be used to build the rest of the mean matrix analogously.

>>>>

We characterize the numbers of constructors that a random generator produces in
the $n$-th generation as a vector $G_n$, a vector that groups the number of
constructors of each kind produced in that generation---in our |Html| example,
this vector has four components, i.e., one for each constructor.
%
%We note $G_n$ to the vector of real numbers that represents the distribution of
%
From branching processes theory, the following equation captures the expected
distribution of constructors at the generation $n$, noted $E[G_n]$, as follows:
%
\begin{align}
  E[G_n]^T = E[G_0]^T \cdot M^n
  \label{eqn:prediction}
\end{align}
%
Vector $E[G_0]$ represents the initial distribution of constructors that our
generator produces, which simply consists of the generation probability of each
one.
%
The interesting aspect of the prediction mechanism is encoded in the matrix $M$,
known as a the \emph{mean matrix} of this stochastic process.
%
$M$ is a squared matrix with as rows and columns as different data constructors
involved in the generation process.
%
Each element $M_{i,j}$ of this matrix encodes the average number of data
constructors of kind $j$ that gets generated in a given generation, provided that we
generated a constructor of kind $i$ at the previous one.
%
In this sense, this matrix encodes the ``branching'' behavior of our random
generation from one generation to the next one.
%
Each element of the matrix can be automatically calculated by exploiting ADT
definitions, % \cite{DBLP:conf/haskell/MistaRH18}
%
% ---specially the recursive fields---
%
as well as the individual probability of generating each constructor.
%
For instance, the average number of |Text| data constructors that we will
generate provided that we generated a |Join| constructor on the previous
level results:
%
$$ M_{\mathrm{Join, Text}} = 2\cdot p_{\mathrm{Text}} $$

where $2$ is the number of holes present when generating a partial ADT value
|Join| (i.e., |Join hole hole|) and $p_{\mathrm{Text}}$ is the probability of
individually generating the constructor |Text|.
%
This reasoning can be used to build the rest of the mean matrix analogously.
